Corona of an M7 fast rotator with a high latitude flare

### 2023-04-17 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure*}[ht!]
    \script{FIGURE_periodograms_xray_and_optical.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/periodogram_om.png}
        \caption{
         MOS and PN light curves stacked Lomb-Scargle periodogram.
        }
        \label{fig:coherence_hist}
    \end{centering}
\end{figure*}

@@

>>>>

\begin{table}

    \caption{TIC 277539431 (WISEA J105515.71-735611.3)}
    \begin{tabular}{l|r}
         Parameter & Value  \\\hline\hline 
         Distance & $13.70\pm0.11\,$pc [2] \\
         $K_s$ mag & $9.666 \pm 0.024$ [3]\\
         $J$ mag & $10.630 \pm 0.023$ [3] \\
         SpT & M7 [1]\\
         Rotation period & $273.618 \pm 0.007\,$min [1]\\
         $v\sin i$ & $38.6\pm1.0\,$km/s [1] \\
         Inclination & $87.0^{+2.0}_{-2.4}\,$ deg [1]\\
         Radius & $0.145\pm0.004\,R_\odot$ [1]\\
         TESS flaring rate $\beta$ &  \\

    \end{tabular}
    \newline\footnotesize
    [1] \citet{ilin2021giant}, [2] \citet{bailer-jones2018estimating}, [3] 2MASS, \citet{skrutskie2006two}
    \label{tab:modelparams}
\end{table}

@@

\begin{figure*}[ht!]
    \script{FIGURE_periodograms_xray_and_optical.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/periodogram_om.png}
        \caption{
         OM light curve Lomb-Scargle periodogram.
        }
        \label{fig:coherence_hist}
    \end{centering}
\end{figure*}

@@

\begin{figure}[ht!]
    \script{FIGURE_data_resid.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/pn_onlyflare1_data_resid.png}
        \caption{
         Flare only PN spectrum fit
        }
        \label{fig:spec_pn_onlyflare}
    \end{centering}
\end{figure}
